Sulfur Dioxide on Water's Surface

### 2011-06-28 Article.tex
New image for the spherical angle definition, fleshed out the section describing the angles theta and phi for orientation analysis. Added bibliography for citations
New transit so2 angle analysis files - not yet added
New cycle results
Rearranging the filenames and working on the h2o-orientation results
New density plots and wrapped up most of the density results section.
changed the title
wrote the conclusions, added some material in the density results.
Rewrote the introduction to ask questions and emphasize the importance of the work, as per Geri's request
rearranged sections per notes from

\usepackage {amsmath}
\usepackage{setspace}

@@

\title{Sulfur Dioxide at Water's Surface}
\author{Eric S. Shamay \and Kevin E. Johnson \and Geraldine L. Richmond}

\begin{document}
\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}

\maketitle

\onehalfspacing

\begin{abstract}
	...Abstract goes here...
\end{abstract}

\include{Introduction}
\include{Background}
\include{Methods}
\include{SteeredMDResults}
\include{EquilibratedResults}

>>>>

\usepackage {amsmath}
\usepackage {setspace}
\usepackage [pdftex]{graphicx}
\usepackage[sort&compress]{achemso}
\usepackage{lineno}

@@

\title{Sulfur Dioxide on Water's Surface}
\author{Eric S. Shamay \and Kevin E. Johnson \and Geraldine L. Richmond}

\begin{document}

\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}

%\maketitle

%\onehalfspacing
\linenumbers 
\doublespacing

\begin{abstract}
Sulfur dioxide binding to water surfaces is a model system for the study of gaseous adsorption processes on aqueous systems. Equilibrium and adsorbing \suldiox~molecules in a pure water interfacial system are modeled by classical molecular dynamics simulations using fully polarizable models for both \suldiox~and \wat. Neat-water systems with a single \suldiox, and high \suldiox~concentration saturated water systems are modeled at equilibrium and using steered molecular dynamics (SMD) to ascertain the orientational profile of a transiting \suldiox~molecule. Orientational depth profiling reveals the preferred orientations of \suldiox~during adsorption, and the complementary behaviors of surface waters adsorbing the gaseous solute.
\end{abstract}

\include{Introduction}
\include{Methods}
\include{Results}
\include{Conclusions}

\bibliography{bib/SulfurDioxideText}

### 2011-06-28 Conclusions.tex
Draft 7 and a new abstract!

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/angle-cartoons/system-surface.png}
		\caption{\wat~and \suldiox~both exhibit preferred orientations in the region near the liquid-gas interface. The neat-water system (A) with a single \suldiox~molecule (low-concentration) has surface waters orienting mostly flat to the interface. When the \suldiox~concentration is increased, as in the saturated system (B), the waters at the surface behave similar to the neat-water interface, but waters that venture into the adsorbed \suldiox~gas layer orient strongly with their bisectors pointing out from the aqueous phase towards the gas. In both cases, the \suldiox~orients with its molecular bisector pointing out to the gas phase when it is near the surface.}
		\label{fig:so2-surface-cartoon}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/angle-cartoons/system-surface.png}
		\caption{\wat~and \suldiox~both exhibit preferred orientations in the region near the liquid-gas interface. The neat-water system (A) with a single \suldiox~molecule (low-concentration) has surface waters orienting mostly flat to the interface. When the \suldiox~concentration is increased, as in the saturated system (B), the waters at the surface behave similar to the neat-water interface, but waters that venture into the adsorbed \suldiox~gas layer orient strongly with their bisectors pointing out from the aqueous phase towards the gas. In both cases, the \suldiox~orients with its molecular bisector pointing out to the gas phase when it is near the surface, and isotropically further into the gas phase. Sulfur, oxygen and hydrogen atoms are colord yellow, red, and white, respectively.}
		\label{fig:so2-surface-cartoon}
	\end{center}
\end{figure}
